Toxic Code Snippets on Stack Overflow

### 2018-11-18 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Updated the Intro.

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software
Engineering. This is a minor revision the submission
no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for
taking their time to read our paper carefully. With their useful and
constructive reviews, we improved the work further by adding xxx minor
improvements as listed below to our previous submission as discussed later in this letter.

\begin{enumerate}
	\item A
	\item B
\end{enumerate}

>>>>

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software
Engineering. This is a minor revision of the submission
no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers again for
taking their time to read our response letter and the paper carefully. With their useful and
constructive reviews, we improved the work further by revising several sections in the paper, 
specifically the two points listed below. Our full responses to the reviewers' comments can be found on the next pages in this letter.

\begin{enumerate}
	\item We softened the claims in the Abstract and Introduction to better reflect the results presented in the paper.
	\item We revised the definition of ``toxic code snippets.''
	\item We clarified the experimental method that we conducted regarding the validation and classification of outdated code snippets.
\end{enumerate}
